Scalar Items in Embedded Position: {A}n Experimental Revisit

### 2012-08-05 text/paper/paper1.tex
paper1 general stuff, typos, layout, minor in whole document

\begin{abstract}
  \dots make concrete \dots
\end{abstract}

@@

\noindent The classical explanation of this inference, following the
pioneering work of \citet{Grice1975:Logic-and-Conve} \citep[see][for
recent overview]{Geurts2010:Quantity-Implic}, is that
(\ref{bsp:Plain-SI-Implicature}) is a pragmatic inference, a so-called
\emph{quantity implicature}, derived by an abductive inference as the
best explanation of why an informed, knowledgable and cooperative
speakers have uttered (\ref{bsp:Plain-SI-Target}) when they could also
have uttered the semantically stronger and relevant
(\ref{bsp:Plain-SI-Alternative}).

@@

\noindent Given this relative abundance of theoretically conceivable
readings, two interlocked empirical questions arise:
\begin{enumerate}[Q1:]
\item which of these three
conceivable readings are available to na\"{i}ve subjects; and
\item which of the available readings are preferred.\fn{It may
    ultimately be impossible to keep unavailability and strong
    dispreference strictly apart. For our purposes this is not
    important. Every time we speak of availability, the so-inclined
    reader may think of non-negligible preference.}
\end{enumerate}
Addressing these questions empirically is relevant because they lie at
the heart of the current debate about the exact location and nature of
the interface between semantics and pragmatics. The controversy
concerns the question to what extent the upper-bounding inference from
\emph{some} to \emph{some but not all} is conventionalized within the
compositional computation of semantic values. For that matter, it is
particularly relevant to assess the availability and relative
preference of local readings. %(Section~\ref{sec:theories-predictions}
%will discuss the relevant theoretical positions and the significance
%of alleged local readings in more detail.)

@@

A number of empirical studies have already examined the availability
of readings for \as- and \es-sentences
\citep[e.g.][]{GeurtsPouscoulous2009:Embedded-Implic,CliftonDube2010:Embedded-Implic,ChemlaSpector2010:Experimental-Ev}. However,
results have not been as clear-cut as one might have hoped for: for
instance, the available empirical evidence is inconclusive as to
whether local readings exist \citep[see also][for related
discussion]{Tielvan-Tiel2012:Embedded-Scalar}, and previous studies 
did not explicitly address all preference relations between readings relevant to
distinguish between theoretical positions. In the following, we will
argue that these heterogeneous results were partly due to the use of 
standard procedures such as picture-verification paradigm, which might not 
be sufficiently sensitive for the phenomenon under investigation,
for instance, due to possible confounding effects of the pictures used.

% We hypothesized that previous studies might be
% insufficiently informative because of the focus on (variants of) a
% picture-verification paradigm.\dn{relate to Bob van Tiel's work} The
% problem is that in order to test the availability of different
% candidate meanings different pictures have to be presented, so that
% effects of pictorial complexity or stereotypicality could never be
% ruled out entirely.
Moreover, previous studies have only accumulated limited evidence
pertaining to the second question that may help decide between
theoretical positions, namely which of the attested readings subjects
prefer. Finally, previous studies presented target sentences
visually. But as it is often argued that focal stress on an
embedded scalar item can favor a local reading
\citep[e.g.][]{Horn2006:The-Border-Wars,Geurts2009:Scalar-Implicat,ChemlaSpector2010:Experimental-Ev,Geurts2010:Quantity-Implic,Tielvan-Tiel2012:Embedded-Scalar},
it seems important to present target sentences auditorily, so as to be
able to control for effects of ``silent prosody'' that subjects may
apply when reading a sentence see Bader 1998, \citep{Fodor1998:Learning}
\dn{provide
  references}.

In reaction to this situation, we therefore presented sentence
materials auditorily and also employed a different kind of visual
presentation of the pictorial material.
%: subjects were presented with
%pictures that were initially covered and could incrementally be
%uncovered at the subjects' request; at each step of uncovering,
%subjects had to decide whether they could already give a truth-value
%judgement or needed more information (Comry ????)\dn{insert
%  references}. 
This way we obtained behavioral data that is both
indicative of the reading subjects assumed and independent of the
potential pictorial and prosodic confounds. 
%At the same time, we hypothesized
%that the incremental nature of this task would shed light on the
%preferences over readings, because the temporal distribution of
%truth-value judgments would give away which reading subjects were
%waiting to evaluate, so to speak. 
Adding to previous studies, we made sure that our method is able 
to reveal information about reading preferences by relating our 
targets to strucutres that are known in the psycholinguistic 
literature for exhibiting certain preferences.

@@

We consider three main theoretical positions which make different
predictions about the readings of \as- and \es-sentences
\citep[c.f.][for
overview]{Horn2006:The-Border-Wars,Geurts2010:Quantity-Implic,Sauerland2012:The-Computation}. We
will refer to these here as \mymark{traditionalism},
\mymark{conventionalism} and \mymark{grammaticalism} and treat each
one in turn. Since there is some leeway in assessing the predictions
for some of these positions (depending on which of several reasonable
additional assumptions we should adopt), we will distinguish different
varieties of each position. For convenience, the predictions of each
(variety of each) position are also summarized in
Table~\ref{tab:predictions} at the end of this section.\dn{micha says:
I'll leave all the varieties in here until we know which ones we need
and which ones we don't need}

@@

Which of these readings, if any, does traditionalism predict to be
preferred? This depends on whether the auxiliary assumptions necessary
to derive global readings by the Gricean recipe are plausibly met in
the particular case of utterance of \as- and \es-sentences. These
auxiliary assumptions include relevance of the extra information
provided in the global reading, mutual awareness that the stronger
alternative has been a speaker option, the speaker's competence about
the issue, etc. Normally, traditionalist accounts would assume that
these extra assumptions are met. In that case, traditionalism would
predict that the global readings should be preferred over the literal
readings. On the other hand, it might also be hypothesized that, for
example, a competence assumption is harder to justify for \as- and
\es-sentences in general than for simpler sentences such as
(\ref{bsp:Plain-SI}), because of the additional quantificational
element: it might be less clear that the speaker knows exactly how
many students solved how many problems, than that the speaker knows
exactly how many problems, e.g., Hans solved. In that case, or if any
other assumption of the Gricean recipe cannot be maintained,
traditionalism would predict that the literal reading would be
preferred over the global one. But that means that there are at least
two varieties of traditionalism that, depending on which additional
assumptions we would make, yield slightly different predictions:
\mymark{the strong variety of traditionalism} maintains that the
auxiliary assumptions of the Gricean recipe hold
usually/strongly/unless-completely-intenable and therefore predicts
that global readings are preferred over the literal ones; \mymark{the
  weak variety of traditionalism} holds that the auxiliary assumptions
are more fragile and predicts that literal readings are preferred over
the global ones.\fn{We mention for clarity that although weak
  traditionalism does not predict the global reading to be preferred,
  it might still predict an \emph{epistemically weak implicature},
  similar to the global reading, that the speaker is uncertain whether
  the stronger alternative is true. Whether it does predict that
  depends on which auxiliary assumption are assumed to be met and
  which are not.}\dn{acknowledge comment by Philippe Schlenker
  here;possibly expand}

Does traditionalism also predict local readings to be available?  The
answer is slightly different for \as- and the \es-sentences. For
\es-sentences, traditionalism does not predict that a local reading is
available, at least not as a quantity implicature
\citep[c.f.][]{GeurtsPouscoulous2009:Embedded-Implic,ChemlaSpector2010:Experimental-Ev}. This
is because traditionalism assumes that quantity implicatures are
pragmatic enrichments of the literal meaning of an utterance, obtained
by conjoining the literal meaning with a suitable set of negated
alternatives. But since the literal and the local reading of
\es-sentences are logically independent, there is no way that local
readings can be derived in a traditionalist manner as a quantity
implicature: if $X$ and $Y$ are logically independent propositions,
then there is no proposition $Z$ such that $X$ would be equivalent to
$Y \wedge \neg Z$. Traditionalism often does concede that (something
like) local readings can occur if scalar items are marked with
\emph{special accentuation}, albeit then as a signal of a different
pragmatic process
\citep[e.g.][]{Horn2006:The-Border-Wars,Geurts2009:Scalar-Implicat,Geurts2010:Quantity-Implic}. We
will come back to this issue in Section~\ref{sec:role-intonation}.

@@

Lexical conventionalism is a position that has been defended for
instance by \citet{LevinsonPresumptiveMeanings2000} and
\citet{Chierchia:2004_ScalarImplicatures}.\fn{See also
  \citet{Sauerland2012:The-Computation} who argues quite favorably for
  a pragmatically informed conventionalism, although eventually
  dismissing it in favor of grammaticalism.} The general idea is that
if the upper-bounding inference from \emph{some} to \emph{some but not
  all} occurs frequently, then it would be inefficient to execute the
Gricean reasoning that traditionalists propose over and over
again. Conventionalism therefore assumes that scalar inferences have
become routinized, hard-wired, so much so that there are two lexical
entries for a scalar item like \emph{some}, one with meaning
\emph{some and maybe all} and one with the meaning \emph{some but not
  all}. \citet{LevinsonPresumptiveMeanings2000} proposed that the
latter is the preferred default meaning, a position which we will
refer to as \mymark{defaultism}.\fn{Levinson's defaultism has strong
  empirical evidence against it, because several processing studies
  show that the computation of scalar inferences appears to be time-
  and effort-consuming, when they \emph{do} arise, not when they
  \emph{don't}, as defaultism would have it
  \citep[c.f.][]{BrehenyKatsos2006:Are-Generalised,BrehenyKatsos2008:Experimental-In,NeysDe-NeysSchaeken2007:When-People-Are}. But
  there is also competing evidence that scalar inferences are
  immediate, low-level processes
  \citep{GrodnerKlein2010:Some-and-Possib}.}\dn{Petra says: empirical
  stuff in footnote irrelevant; I agree, let's move it to discussion
  section} For completeness sake, we will call the opposite view that
the literal meanings are \emph{ceteris paribus} preferred
\mymark{literalism}\dn{better name?}. We are not aware that anyone has
defended this option, but we will come back to this later on.\dn{where
  exactly}

Both varieties of conventionalism make interesting predictions about
available readings for \as- and \es-sentences. Unaided,
conventionalism does not predict that global readings are
available. The lexically stored upper-bound for scalar \emph{some}
only allows to derive literal and local readings. Moreover, defaultism
predicts that local readings are preferred over literal ones. Contrary
to that, our dummy position of literalism predicts that literal
readings are preferred over local ones.\dn{Petra says that his is too
  short; suggests skipping the whole section; I'm not sure; could do
  that too; anyway, it must be mentioned because conventionalism turns
  out to be one of the best predictors of our data;}

@@

The third and final kind of theoretical position we consider is
\mymark{grammaticalism}. Recently, a lot of evidence based on
intuitive judgements and more theoretical considerations has been
discussed in favor of this position
\citep[c.f.][]{Chierchia2006:Broaden-Your-Vi,Fox2007:Free-Choice-and,Magri2011:Another-Argumen,Sauerland2012:The-Computation,ChierchiaFox2008:The-Grammatical,Chierchia2012:FC-Nominals-and}. % When
% it comes to the predictions of available readings of \as- and
% \es-sentences, grammaticalism appears like the conjunction of
% traditionalism and conventionalism. But conceptually speaking,
% grammaticalism goes down a road of its own.
Grammaticalism approaches quantity implicatures by postulating a
silent operator that can be variably applied during compositional
computation of a sentence's truth-value
\citep{Chierchia2006:Broaden-Your-Vi}, if necessary multiple times
\citep{Fox2007:Free-Choice-and}. This silent operator is variably
referred to as $\mathrm{O}(\cdot)$ or $\exh(\cdot)$, because it is
assumed to be similar in effect to the meaning of particle \emph{only}
or of the mechanism of \emph{exhaustive interpretation}
\citep{GroenendijkStokhofThesis1984,Stechowvon-StechowZimmermann1984:Term-Answers-an,Rooijvan-RooijSchulz2013:Exhaustive-Inte,vanRooijSchulz:ExhaustiveInterpretation,Fox2007:Free-Choice-and}. For
our purposes, it is enough to note that $\exh(\cdot)$ is a
poly-typed function that enriches an expression $X$, which crucially
need not be a full proposition, based on a set, $\alt(X)$, of
(suitable, relevant) alternatives to $X$ that yields an enriched
meaning of the form:\fn{More sophisticated formulations of exhaustive
  interpretation have been proposed
  \citep[e.g.][]{Schulz2005:A-Pragmatic-Sol,vanRooijSchulz:ExhaustiveInterpretation,Spector2006:Scalar-Implicat,Fox2007:Free-Choice-and}
  but this simple formulation is sufficient for the purposes of this
  paper. Also, we gloss here over non-trivial details in the way this
  operation is to be specified exactly within a compositional
  semantics \citep[c.f.][]{Chierchia2006:Broaden-Your-Vi}.}
\begin{exe}
  \ex \label{bsp:Exh-Def} $\exh(X,\alt(X)) = X \bigwedge_{A \in
      \alt(X)} \neg A$.
\end{exe}

@@

To account for the markedness of certain examples, grammaticalism is
therefore aided by a principle that specifies which readings are to be
preferred if several readings are generated by optional applications
of $\exh(\cdot)$ in the compositional computation of semantic
values. The principle that grammaticalists adhere to
\citep[c.f.][]{FoxSpector:Economy-and-Emb,ChierchiaFox2008:The-Grammatical,Chierchia2012:FC-Nominals-and}
is the \mymark{strongest meaning hypothesis} of
\citet{DalrympleKanazawa1998:Reciprocal-Expr}. Roughly speaking, if a
given sentence has several conceivable readings, the strongest meaning
hypothesis selects for the strongest of
these. \citet{ChierchiaFox2008:The-Grammatical} discuss two concrete
variants of the strongest meaning hypothesis. Towards a definition
that is just precise enough for our current purposes, fix a sentence
with propositional content $S$ with candidate readings $C(S)$, where
$C(S)$ contains $S$ and all readings derivable from inserting
$\exh(\cdot)$ at suitable scope sites.\fn{Strictly speaking, we should
  compare \emph{parses} of sentences with $\exh(\cdot)$ at various
  scope sites with respect to the readings that these parses give rise
  to \citep[c.f.][]{ChierchiaFox2008:The-Grammatical}, but we may
  ignore this detail here for ease of exposition.}  Then define
\emph{ceteris paribus} preferences among members of $X,Y \in C(S)$ as
either:
\begin{exe}
\ex \label{bsp:SMH-Total} 
  $X >_w Y$ iff $X \subset Y$ 
  \attrib{\citep[(104)]{ChierchiaFox2008:The-Grammatical}}
\end{exe}
or:
\begin{exe}
\ex \label{bsp:SMH-Partial}  $X >_s Y$ iff $X \subset Y$ and $X$ and
  $Y$ are readings obtained from applications of $\exh(\cdot)$ at
  exactly the same scope sites, except for one.
  \attrib{\citep[(105)]{ChierchiaFox2008:The-Grammatical}} 
\end{exe}
Since $X >_s Y$ entails $X >_w Y$, we will speak of \mymark{weak
  grammaticalism} and \mymark{strong grammaticalism}, depending on
whether (\ref{bsp:SMH-Total}) or (\ref{bsp:SMH-Partial}) is used.

@@

\noindent That the majority answer is ``both'' could be taken as
evidence that the literal reading is the preferred one. But the almost
40\% of choices for the strong situation, so
\citeauthor{CliftonDube2010:Embedded-Implic} argue, might be
indicative of the availability of the local reading. In version 2 of
the experiment, the picture pair consisted of the literal and weak
situations in Figures~\ref{fig:literal-AE} and \ref{fig:weak}. In this
case, response percentages were:

@@

Taken together, the results by Clifton and Dube demonstrate that
participants' choices for \as-readings might be strongly affected by
the specific experimental paradigm used. If task demands are only
felicitous for a literal reading, the \emph{absence} of choices of
local readings cannot be accounted for by assuming an inavailability
of these readings \emph{per se}.\dn{micha does not understand this
  sentence} However, at present it is less clear whether these results
can also be generalized to further situations. For instance, subjects
rejected the \es-sentences in Geurts and Poscoulous' original study,
despite the fact that they could have accepted them based on the local
reading. It is thus necessary to test both universal and non-monotonic
quantifiers within the same experiment using a task that offers
alternatives. Additionally, it would be informative to also probe into
the availability and the relative preference of global readings. The
study of \citet{ChemlaSpector2010:Experimental-Ev} did both of that.

@@

\citeauthor{ChemlaSpector2010:Experimental-Ev} hypothesized that the
degree to which a sentence is rated acceptable is proportional to the
number of available true readings. Observed averaged clicking
positions are shown in Figures~\ref{fig:CS-Results-as} and
\ref{fig:CS-Results-es}.
%
% \begin{figure}
%   \centering
%   \subfloat[][\as-condition]{
%     \label{fig:CS-Results-as}
%         \includegraphics[width=5.5cm]{../pictures/paper/Chemla_Spector_2010_Results_AE.png}
%   }
%   \subfloat[test][\es-condition]{
%     \label{fig:CS-Results-es}
%     \includegraphics[width=5.5cm]{../pictures/paper/Chemla_Spector_2010_Results_GE.png}
%   }
%   \caption{Results from
%     \citeauthor{ChemlaSpector2010:Experimental-Ev}'s
%     (\citeyear{ChemlaSpector2010:Experimental-Ev}) study}
%   \label{fig:Chemla-Spector-Results}
% \end{figure}
%
According to \citeauthor{ChemlaSpector2010:Experimental-Ev}, the
crucial piece of evidence for the availability of local readings for
\as-sentences is that these sentences yielded higher graded
acceptability scores for the strong situation than for the weak
situation (although these differ only with respect to the truth value
of the local reading). In a similar way, evidence for the availability
of the local reading for \es-sentences comes from the difference
between the local and the literal situation. Strikingly, \es-sentences
received an average 73\% degree of acceptability in the local
situation although the literal and global readings are false in this
case.

@@

\begin{table}[ht]
	\centering
	\subfloat[][\as-Sentences]{ 
\begin{tabular}{cccc}
&more info&true&false\\ \midrule
Step 1&error&\lit&error\\
Step 2&error&\glb&error\\
Step 3&-&error&\loc
\end{tabular}

>>>>

\begin{abstract}
  \begin{itemize}
  \item What is needed to complement the picture is data from a
    verification experiment that is as independent as possible of
    potentially conflating properties of the pictorial material and
    that is nonetheless sensitive enough to detect local readings even
    if they are dispreferred.
  \end{itemize}

\end{abstract}

@@

\noindent The classical explanation of this inference, following the
pioneering work of \citet{Grice1975:Logic-and-Conve} \citep[see][for
recent overview]{Geurts2010:Quantity-Implic}, is that
(\ref{bsp:Plain-SI-Implicature}) is a pragmatic inference, a so-called
\emph{quantity implicature}, derived by an abductive inference as the
best explanation of why informed, knowledgable and cooperative
speakers would utter (\ref{bsp:Plain-SI-Target}) when they could also
utter the semantically stronger and relevant
(\ref{bsp:Plain-SI-Alternative}).

@@

\noindent Given this relative abundance of theoretically conceivable
readings, two interlocked empirical questions arise:
\begin{enumerate}[Q1:]
\item which of these readings are available to na\"{i}ve subjects; and
\item which of the available readings are preferred.\fn{It may
    ultimately be impossible to keep unavailability and strong
    dispreference strictly apart. For our purposes this is not
    important. Every time we speak of availability, the so-inclined
    reader may think of non-negligible preference.}
\end{enumerate}
Addressing these questions empirically is relevant because they lie at
the heart of the current debate about the exact location and nature of
the interface between semantics and pragmatics. The controversy
concerns the question to what extent the upper-bounding inference from
\emph{some} to \emph{some but not all} is conventionalized within the
compositional computation of semantic values. For that matter, it is
particularly relevant to assess the availability and relative
preference of local readings. %(Section~\ref{sec:theories-predictions}
%will discuss the relevant theoretical positions and the significance
%of alleged local readings in more detail.)

@@

A number of empirical studies have already examined the availability
of readings for \as- and \es-sentences
\citep[e.g.][]{GeurtsPouscoulous2009:Embedded-Implic,CliftonDube2010:Embedded-Implic,ChemlaSpector2010:Experimental-Ev}. However,
results have not been as clear-cut as one might have hoped for: for
instance, the available empirical evidence is inconclusive as to
whether local readings exist \citep[see also][for related
discussion]{Tielvan-Tiel2012:Embedded-Scalar}, and previous studies 
did not explicitly address all preference relations between readings relevant to
distinguish between theoretical positions. In the following, we will
argue that these heterogeneous results were partly due to the use of 
standard procedures such as picture-verification paradigm, which might not 
be sufficiently sensitive for the phenomenon under investigation,
for instance, due to possible confounding effects of the pictures used.
% We hypothesized that previous studies might be
% insufficiently informative because of the focus on (variants of) a
% picture-verification paradigm.\dn{relate to Bob van Tiel's work} The
% problem is that in order to test the availability of different
% candidate meanings different pictures have to be presented, so that
% effects of pictorial complexity or stereotypicality could never be
% ruled out entirely.
Moreover, previous studies have only accumulated limited evidence
pertaining to the second question that may help decide between
theoretical positions, namely which of the attested readings subjects
prefer. Finally, previous studies presented target sentences
visually. But as it is often argued that focal stress on an
embedded scalar item can favor a local reading
\citep[e.g.][]{Horn2006:The-Border-Wars,Geurts2009:Scalar-Implicat,ChemlaSpector2010:Experimental-Ev,Geurts2010:Quantity-Implic,Tielvan-Tiel2012:Embedded-Scalar},
it seems important to present target sentences auditorily, so as to be
able to control for effects of ``silent prosody'' that subjects may
apply when reading a sentence see Bader 1998, \citep{Fodor1998:Learning}
\dn{provide
  references}.

In reaction to this situation, we therefore presented sentence
materials auditorily and also employed a different kind of visual
presentation of the pictorial material.
%: subjects were presented with
%pictures that were initially covered and could incrementally be
%uncovered at the subjects' request; at each step of uncovering,
%subjects had to decide whether they could already give a truth-value
%judgement or needed more information (Comry ????)\dn{insert
%  references}. 
This way we obtained behavioral data that is both
indicative of the reading subjects assumed and independent of the
potential pictorial and prosodic confounds. 
%At the same time, we hypothesized
%that the incremental nature of this task would shed light on the
%preferences over readings, because the temporal distribution of
%truth-value judgments would give away which reading subjects were
%waiting to evaluate, so to speak. 
Adding to previous studies, we made sure that our method is able to
reveal information about reading preferences by relating our targets
to ambiguous sentences with a well-known preference on available
readings.

@@

We consider three main theoretical positions which make different
predictions about the readings of \as- and \es-sentences
\citep[c.f.][for
overview]{Horn2006:The-Border-Wars,Geurts2010:Quantity-Implic,Sauerland2012:The-Computation}. We
will refer to these here as \mymark{traditionalism},
\mymark{conventionalism} and \mymark{grammaticalism} and treat each
one in turn. Since there is some leeway in assessing the predictions
for each of these positions (depending on which of several reasonable
additional assumptions we should adopt), we will distinguish different
varieties of each. For convenience, the predictions of each (variety
of each) position are also summarized in Table~\ref{tab:predictions}
at the end of this section.\dn{micha says: I'll leave all the
  varieties in here until we know which ones we need and which ones we
  don't need}

@@

Which of these readings, if any, does traditionalism predict to be
preferred? This depends on whether the auxiliary assumptions necessary
to derive global readings by the Gricean recipe are plausibly met in
the particular case of utterance of \as- and \es-sentences. These
auxiliary assumptions include relevance of the extra information
provided in the global reading, mutual awareness that the stronger
alternative has been a speaker option, the speaker's competence about
the issue, etc. Normally, traditionalist accounts would assume that
these extra assumptions are met. In that case, traditionalism would
predict that global readings should be preferred over literal
readings. On the other hand, it might also be hypothesized that, for
example, a competence assumption is harder to justify for \as- and
\es-sentences in general than for simpler sentences such as
(\ref{bsp:Plain-SI}), because of the additional quantificational
element: it might be less clear that the speaker knows exactly how
many students solved how many problems, than that the speaker knows
exactly how many problems, e.g., Hans solved. In that case, or if any
other assumption of the Gricean recipe cannot be maintained,
traditionalism would predict that the literal reading would be
preferred over the global one. But that means that there are at least
two varieties of traditionalism that, depending on which additional
assumptions we would make, yield slightly different predictions:
\mymark{the strong variety of traditionalism} maintains that the
auxiliary assumptions of the Gricean recipe hold
usually/strongly/unless-completely-intenable and therefore predicts
that global readings are preferred over literal ones; \mymark{the weak
  variety of traditionalism} holds that the auxiliary assumptions are
more fragile and predicts that literal readings are preferred over the
global ones.\fn{We mention for clarity that although weak
  traditionalism does not predict the global reading to be preferred,
  it might still predict an \emph{epistemically weak implicature},
  similar to the global reading, that the speaker is uncertain whether
  the stronger alternative is true. Whether it does predict that
  depends on which auxiliary assumptions are assumed to be met and
  which are not.}\dn{acknowledge comment by Philippe Schlenker
  here;possibly expand}

Does traditionalism also predict local readings to be available?  The
answer is slightly different for \as- and the \es-sentences. For
\es-sentences, traditionalism does not predict that a local reading is
available, at least not as a quantity implicature
\citep[c.f.][]{GeurtsPouscoulous2009:Embedded-Implic,ChemlaSpector2010:Experimental-Ev}. This
is because traditionalism assumes that quantity implicatures are
pragmatic enrichments of the literal meaning of an utterance, obtained
by conjoining the literal meaning with a suitable set of negated
alternatives. But since the literal and the local reading of
\es-sentences are logically independent, there is no way that local
readings can be derived in a traditionalist manner as a quantity
implicature: if $X$ and $Y$ are logically independent propositions,
then there is no proposition $Z$ such that $X$ would be equivalent to
$Y \wedge \neg Z$. Traditionalism often does concede that (something
like) local readings can occur if scalar items are marked with
\emph{special accentuation}, albeit then as a signal of a different
pragmatic process
\citep[e.g.][]{Horn2006:The-Border-Wars,Geurts2009:Scalar-Implicat,Geurts2010:Quantity-Implic}. We
will come back to this issue in Section~\ref{sec:local-read-categ}.

@@

Lexical conventionalism is a position that has been defended for
instance by \citet{LevinsonPresumptiveMeanings2000} and
\citet{Chierchia:2004_ScalarImplicatures}.\fn{See also
  \citet{Sauerland2012:The-Computation} who argues quite favorably for
  a pragmatically informed conventionalism, although eventually
  dismissing it in favor of grammaticalism.} The general idea is that
if the upper-bounding inference from \emph{some} to \emph{some but not
  all} occurs frequently, then it would be inefficient to execute the
Gricean reasoning that traditionalists propose over and over
again. Conventionalism therefore assumes that scalar inferences have
become routinized, hard-wired, so much so that there are two lexical
entries for a scalar item like \emph{some}, one with meaning
\emph{some and maybe all} and one with the meaning \emph{some but not
  all}. \citet{LevinsonPresumptiveMeanings2000} proposed that the
latter is the preferred default meaning, a position which we will
refer to as \mymark{defaultism}.\fn{Levinson's defaultism has strong
  empirical evidence against it, because several processing studies
  show that the computation of scalar inferences appears to be time-
  and effort-consuming, when they \emph{do} arise, not when they
  \emph{don't}, as defaultism would have it
  \citep[c.f.][]{BrehenyKatsos2006:Are-Generalised,BrehenyKatsos2008:Experimental-In,NeysDe-NeysSchaeken2007:When-People-Are}. But
  there is also competing evidence that scalar inferences are
  immediate, low-level processes
  \citep{GrodnerKlein2010:Some-and-Possib}.}\dn{Petra says: empirical
  stuff in footnote irrelevant; I agree, let's move it to discussion
  section} For completeness sake, we will call the opposite view that
the literal meanings are \emph{ceteris paribus} preferred
\mymark{literalism}. We are not aware that anyone has defended this
option, but it pays to include this option, because, as we will see
later on, this possible position is the best direct explanation of our
experimental data.

Both varieties of conventionalism make interesting predictions about
available readings for \as- and \es-sentences. Unaided,
conventionalism does not predict that global readings are
available. The lexically stored upper-bound for scalar \emph{some}
only allows to derive literal and local readings. Moreover, defaultism
predicts that local readings are preferred over literal ones. Contrary
to that, our dummy position of literalism predicts that literal
readings are preferred over local ones.

@@

The third and final kind of theoretical position we consider is
\mymark{grammaticalism}. Recently, a lot of evidence based on
intuitive judgements and more theoretical considerations has been
discussed in favor of this position
\citep[c.f.][]{Chierchia2006:Broaden-Your-Vi,Fox2007:Free-Choice-and,Magri2011:Another-Argumen,Sauerland2012:The-Computation,ChierchiaFox2008:The-Grammatical,Chierchia2012:FC-Nominals-and}. % When
% it comes to the predictions of available readings of \as- and
% \es-sentences, grammaticalism appears like the conjunction of
% traditionalism and conventionalism. But conceptually speaking,
% grammaticalism goes down a road of its own.
Grammaticalism approaches quantity implicatures by postulating a
silent operator that can be variably applied during compositional
computation of a sentence's truth-value
\citep{Chierchia2006:Broaden-Your-Vi}, if necessary multiple times
\citep{Fox2007:Free-Choice-and}. This silent operator is variably
referred to as $\mathrm{O}(\cdot)$ or $\exh(\cdot)$, because it is
assumed to be similar in effect to the meaning of particle \emph{only}
or of the mechanism of \emph{exhaustive interpretation}
\citep{GroenendijkStokhofThesis1984,Stechowvon-StechowZimmermann1984:Term-Answers-an,Rooijvan-RooijSchulz2013:Exhaustive-Inte,vanRooijSchulz:ExhaustiveInterpretation,Fox2007:Free-Choice-and}. For
our purposes, it is enough to note that $\exh(\cdot)$ is a
poly-typed function that enriches an expression $X$, which crucially
need not be a full proposition, based on a set $\alt(X)$ of
(suitable, relevant) alternatives to $X$ that yields an enriched
meaning of the form:\fn{More sophisticated formulations of exhaustive
  interpretation have been proposed
  \citep[e.g.][]{Schulz2005:A-Pragmatic-Sol,vanRooijSchulz:ExhaustiveInterpretation,Spector2006:Scalar-Implicat,Fox2007:Free-Choice-and}
  but this simple formulation is sufficient for the purposes of this
  paper. Also, we gloss here over non-trivial details in the way this
  operation is to be specified exactly within a compositional
  semantics \citep[c.f.][]{Chierchia2006:Broaden-Your-Vi}.}
\begin{exe}
  \ex \label{bsp:Exh-Def} $\exh(X,\alt(X)) = X \bigwedge_{A \in
      \alt(X)} \neg A$.
\end{exe}

@@

To account for the markedness of certain examples, grammaticalism is
therefore aided by a principle that specifies which readings are to be
preferred if several readings are generated by optional applications
of $\exh(\cdot)$ in the compositional computation of semantic
values. The principle that grammaticalists adhere to
\citep[c.f.][]{FoxSpector:Economy-and-Emb,ChierchiaFox2008:The-Grammatical,Chierchia2012:FC-Nominals-and}
is the \mymark{strongest meaning hypothesis} of
\citet{DalrympleKanazawa1998:Reciprocal-Expr}. Roughly speaking, if a
given sentence has several conceivable readings, the strongest meaning
hypothesis selects for the strongest of
these. \citet{ChierchiaFox2008:The-Grammatical} discuss two concrete
variants of the strongest meaning hypothesis: fix a sentence with
propositional content $S$ with candidate readings $C(S)$, where $C(S)$
contains $S$ and all readings derivable from inserting $\exh(\cdot)$
at suitable scope sites;\fn{Strictly speaking, we should compare
  \emph{parses} of sentences with $\exh(\cdot)$ at various scope sites
  with respect to the readings that these parses give rise to
  \citep[c.f.][]{ChierchiaFox2008:The-Grammatical}, but we may ignore
  this detail here for ease of exposition.} then define \emph{ceteris
  paribus} preferences among members of $X,Y \in C(S)$ as either
\begin{exe}
\ex \label{bsp:SMH-Total} 
  $X$ is preferred to $Y$ iff $X \subset Y$ 
  \attrib{\citep[(104)]{ChierchiaFox2008:The-Grammatical}}
\end{exe}
or
\begin{exe}
\ex \label{bsp:SMH-Partial}  $X$ is preferred to $Y$ iff $X \subset Y$
  and $X$ and $Y$ are readings obtained from applications of
  $\exh(\cdot)$ at exactly the same scope sites, except for
  one. \attrib{\citep[(105)]{ChierchiaFox2008:The-Grammatical}} 
\end{exe}
Since the former is entailed by the latter, we will speak of
\mymark{weak grammaticalism} and \mymark{strong grammaticalism},
depending on whether (\ref{bsp:SMH-Total}) or (\ref{bsp:SMH-Partial})
is used.

@@

\noindent That the majority answer is ``both'' could be taken as
evidence that the literal reading is the preferred one. But the almost
40\% of choices for the strong situation, so
\citeauthor{CliftonDube2010:Embedded-Implic} argue, is indicative of
the availability of the local reading. In version 2 of the experiment,
the picture pair consisted of the literal and weak situations in
Figures~\ref{fig:literal-AE} and \ref{fig:weak}. In this case,
response percentages were:

@@

The diverging results of
\citeauthor{GeurtsPouscoulous2009:Embedded-Implic} and
\citeauthor{CliftonDube2010:Embedded-Implic} demonstrate that
participants' choices for \as-readings might be strongly affected by
the specific experimental paradigm used. If task demands are only
felicitous for a literal reading, the \emph{absence} of choices of
local readings cannot be accounted for by assuming an unavailability
of these readings \emph{per se}.\dn{micha does not understand this
  sentence} However, at present it is less clear whether these results
can also be generalized to further situations. For instance, subjects
rejected the \es-sentences in Geurts and Poscoulous' original study,
despite the fact that they could have accepted them based on the local
reading. It is thus necessary to test both universal and non-monotonic
quantifiers within the same experiment. Additionally, it would be
informative to also probe into the availability of global
readings. The study of \citet{ChemlaSpector2010:Experimental-Ev} did
both of that.

@@

\citeauthor{ChemlaSpector2010:Experimental-Ev} hypothesized that the
degree to which a sentence is rated acceptable is proportional to the
number of available true readings. Observed averaged clicking
positions are shown in Figures~\ref{fig:CS-Results-as} and
\ref{fig:CS-Results-es}.
%
% \begin{figure}
%   \centering
%   \subfloat[][\as-condition]{
%     \label{fig:CS-Results-as}
%         \includegraphics[width=5.5cm]{../pictures/paper/Chemla_Spector_2010_Results_AE.png}
%   }
%   \subfloat[test][\es-condition]{
%     \label{fig:CS-Results-es}
%     \includegraphics[width=5.5cm]{../pictures/paper/Chemla_Spector_2010_Results_GE.png}
%   }
%   \caption{Results from
%     \citeauthor{ChemlaSpector2010:Experimental-Ev}'s
%     (\citeyear{ChemlaSpector2010:Experimental-Ev}) study}
%   \label{fig:Chemla-Spector-Results}
% \end{figure}
%
According to \citeauthor{ChemlaSpector2010:Experimental-Ev}, the
crucial piece of evidence for the availability of local readings for
\as-sentences is that these sentences yielded higher graded
acceptability scores for the strong situation than for the weak
situation (although these differ only with respect to the truth value
of the local reading). Evidence for the availability
of the local reading for \es-sentences comes from the difference
between the local and the literal situation. Strikingly, \es-sentences
received an average 73\% degree of acceptability in the local
situation although the literal and global readings are false in this
case.

@@

\begin{table}[ht]
	\centering
	\subfloat[][\as-Sentences]{ 
\begin{tabular}{cccc}
&more info&true&false\\ \midrule
Step 1&-&\lit&error\\
Step 2&-&\glb&error\\
Step 3&n.a.&error&\loc
\end{tabular}
